---
title: "Questions"
author: "Cyril Matthey-Doret"
date: "August 17, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
auto_processed <-read.table("/home/cyril/Documents/Internship/Data/R_working_directory/auto/auto_processed_data.csv", header = T, sep= ",")
manual_processed <-read.table("/home/cyril/Documents/Internship/Data/R_working_directory/manual/manual_processed_data.csv", header = T, sep= ",")
library(ggplot2)
library(gridExtra)
library(lattice)
```
# Research Questions

##1. Does reproductive mode affect variables on an overall scale? \newline (Manual + Digitalized)

###From manual dataset:



```{r overall_host_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=6}
par(mfrow = c(1,2))
boxplot(log10(manual_processed[manual_processed$mode!='both',"nbr_host_spp"])~droplevels(manual_processed[manual_processed$mode!='both',"mode"]),
        main="Host species by \nReproductive mode: Overall",
        names=c(paste0("Asex: ","n=",length(manual_processed[manual_processed$mode=="asex" & !is.na(manual_processed$nbr_host_spp),"lat_max"])),paste0("Sex: ","n=",length(manual_processed[manual_processed$mode=="sex" & !is.na(manual_processed$nbr_host_spp),"lat_max"]))), ylab="Number of host species")

mean_length<-(manual_processed[manual_processed$mode!='both',"min_length"]+manual_processed[manual_processed$mode!='both',"max_length"])/2
boxplot(mean_length~droplevels(manual_processed[manual_processed$mode!='both',"mode"]),
        main="Body length by \nReproductive mode: Overall",
        names=c(paste0("Asex: ","n=",length(manual_processed[manual_processed$mode=="asex" & !is.na(manual_processed$min_length),"lat_max"])),paste0("Sex: ","n=",length(manual_processed[manual_processed$mode=="sex" & !is.na(manual_processed$min_length),"lat_max"]))),ylab="Body length [mm]")

```

```{r overall_distribution_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=5}
w <-ggplot()+
  geom_boxplot(data = manual_processed[!is.na(manual_processed$mode) & manual_processed$mode!='both',],aes(x=mode,y=lat_median))+
  ggtitle("Median latitude")+
  labs(x="Reproductive mode",y="Latitude")+
  annotate(x = c(1,2),y=c(30,30),geom= "text", label=c(paste0("n=",length(manual_processed[manual_processed$mode=="asex","lat_max"])),
                                                       paste0("n=",length(manual_processed[manual_processed$mode=="sex","lat_max"]))))+
  theme_bw()

x <- ggplot()+
  geom_boxplot(data = manual_processed[!is.na(manual_processed$mode) & manual_processed$mode!='both',],aes(x=mode,y=pmax(abs(lat_max),abs(lat_min))))+
  ggtitle("Max distance from the equator")+
  labs(x="Reproductive mode",y="Absolute latitude")+
  annotate(x = c(1,2),y=c(43,43),geom= "text", label=c(paste0("n=",length(manual_processed[manual_processed$mode=="asex","lat_max"])),
                                                            paste0("n=",length(manual_processed[manual_processed$mode=="sex","lat_max"]))))+
  theme_bw()

y <- ggplot()+
  geom_boxplot(data = manual_processed[!is.na(manual_processed$mode) & manual_processed$mode!='both',],aes(x=mode,y=pmin(abs(lat_max),abs(lat_min))))+
  ggtitle("Min distance from the equator")+
  labs(x="Reproductive mode",y="Absolute latitude")+
  annotate(x = c(1,2),y=c(28,28),geom= "text", label=c(paste0("n=",length(manual_processed[manual_processed$mode=="asex","lat_max"])),
                                                            paste0("n=",length(manual_processed[manual_processed$mode=="sex","lat_max"]))))+
  theme_bw()


z <- ggplot()+
  geom_boxplot(data = manual_processed[!is.na(manual_processed$mode) & manual_processed$mode!='both'& manual_processed$nbr_country>1,],aes(x=mode,y=lat_max-lat_min))+
  ggtitle("Latitude range")+
  labs(x="Reproductive mode",y="Latitude range")+
  annotate(x = c(1,2),y=c(55,55),geom= "text", label=c(paste0("n=",length(manual_processed[manual_processed$mode=="asex" & manual_processed$nbr_country>1,"lat_max"])),
                                                            paste0("n=",length(manual_processed[manual_processed$mode=="sex"& manual_processed$nbr_country>1,"lat_max"]))))+
  theme_bw()
grid.arrange(w,x,y,z)

```

###From digitalized dataset:

```{r overall_host_auto_repartition, echo=FALSE, error=FALSE, warning=FALSE,fig.height=4,fig.width=5}
par(mfrow=c(1,2))
boxplot(auto_processed[auto_processed$mode!='both' & auto_processed$host_spp>0,"host_spp"]~droplevels(auto_processed[auto_processed$mode!='both' & auto_processed$host_spp>0,"mode"]),
        main="Host species: Overall",
        names=c(paste0("Asex: ","n=",length(auto_processed[auto_processed$mode=="asex" & !is.na(auto_processed$host_spp) & auto_processed$host_spp>0,"lat_max"])),paste0("Sex: ","n=",length(auto_processed[auto_processed$mode=="sex" & !is.na(auto_processed$host_spp) & auto_processed$host_spp>0,"lat_max"]))), ylab="Number of host species")

boxplot(log10(auto_processed[auto_processed$mode!='both' & auto_processed$host_spp>0,"host_spp"])~droplevels(auto_processed[auto_processed$mode!='both' & auto_processed$host_spp>0,"mode"]),
        main="Log10 host species: Overall",
        names=c(paste0("Asex: ","n=",length(auto_processed[auto_processed$mode=="asex" & !is.na(auto_processed$host_spp) & auto_processed$host_spp>0,"lat_max"])),paste0("Sex: ","n=",length(auto_processed[auto_processed$mode=="sex" & !is.na(auto_processed$host_spp) & auto_processed$host_spp>0,"lat_max"]))), ylab="Number of host species")

```

```{r overall_host_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}
ggplot()+
  geom_boxplot(data = auto_processed[!is.na(auto_processed$mode),],aes(x=mode,y=lat_median))+
  ggtitle("Median latitude")+
  labs(x="Reproduction mode",y="Latitude")+
  annotate(x = c(1,2),y=c(28,23),geom= "text", label=c(paste0("n=",length(auto_processed[auto_processed$mode=="asex","lat_max"])),                                                      paste0("n=",length(auto_processed[auto_processed$mode=="sex","lat_max"]))))+
  theme_bw()
```


```{r overall_distribution_auto, echo=FALSE, error=FALSE, warning=FALSE, fig.height=8,fig.width=8}
max_equ <-ggplot()+
geom_boxplot(data = auto_processed[!is.na(auto_processed$mode),],aes(x=mode,y=pmax(abs(lat_max),abs(lat_min))))+
  ggtitle("Maximum distance from the equator")+
  labs(x="Reproduction mode",y="Absolute latitude")+
  annotate(x = c(1,2),y=c(52,42),geom= "text", label=c(paste0("n=",length(auto_processed[auto_processed$mode=="asex","lat_max"])),                                                      paste0("n=",length(auto_processed[auto_processed$mode=="sex","lat_max"]))))+
  theme_bw()

min_equ <-ggplot()+
  geom_boxplot(data = auto_processed[!is.na(auto_processed$mode),],aes(x=mode,y=pmin(abs(lat_max),abs(lat_min))))+
  ggtitle("Minimum distance from the equator")+
  labs(x="Reproduction mode",y="Latitude")+
  annotate(x = c(1,2),y=c(27,35),geom= "text", label=c(paste0("n=",length(auto_processed[auto_processed$mode=="asex","lat_max"])),                                                       paste0("n=",length(auto_processed[auto_processed$mode=="sex","lat_max"]))))+
  theme_bw()
  
median_equ <-ggplot()+
  geom_boxplot(data = auto_processed[!is.na(auto_processed$mode),],aes(x=mode,y=lat_median))+
  ggtitle("Median latitude")+
  labs(x="Reproduction mode",y="Latitude")+
  annotate(x = c(1,2),y=c(28,23),geom= "text", label=c(paste0("n=",length(auto_processed[auto_processed$mode=="asex","lat_max"])),                                                      paste0("n=",length(auto_processed[auto_processed$mode=="sex","lat_max"]))))+
  theme_bw()

latrange_equ <-ggplot()+
  geom_boxplot(data = auto_processed[!is.na(auto_processed$mode) & auto_processed$nbr_country>1,],aes(x=mode,y=pmin(lat_max-lat_min)))+
  ggtitle("Latitude range")+
  labs(x="Reproduction mode",y="Latitude")+
  annotate(x = c(1,2),y=c(58,21),geom= "text", label=c(paste0("n=",length(auto_processed[auto_processed$mode=="asex" & auto_processed$nbr_country>1,"lat_max"])),                                                      paste0("n=",length(auto_processed[auto_processed$mode=="sex" & auto_processed$nbr_country>1,"lat_max"]))))+
  theme_bw()

grid.arrange(median_equ, max_equ, min_equ, latrange_equ)

```

###Comparison: number of locations, study bias

```{r study_bias_nbr_country}
par(mfrow=c(1,2))
boxplot(
  log10(auto_processed$nbr_country[auto_processed$nbr_country>0 & auto_processed$mode=="asex"]),
  log10(auto_processed$nbr_country[auto_processed$nbr_country>0 & auto_processed$mode=="sex"]),main= "Number of countries: Overall, auto dataset",ylab="Log ratio",names=c(paste0("Asex: n=",length(auto_processed$nbr_country[auto_processed$nbr_country>0 & auto_processed$mode=="asex"])),paste0("Sex: n=",length(auto_processed$nbr_country[auto_processed$nbr_country>0 & auto_processed$mode=="sex"])))
)
boxplot(
  log10(manual_processed$nbr_country[manual_processed$nbr_country>0 & manual_processed$mode=="asex"]),
  log10(manual_processed$nbr_country[manual_processed$nbr_country>0 & manual_processed$mode=="sex"]),main= "Number of countries: Overall, manual dataset",ylab="Log ratio",names=c(paste0("Asex: n=",length(manual_processed$nbr_country[manual_processed$nbr_country>0 & manual_processed$mode=="asex"])),paste0("Sex: n=",length(manual_processed$nbr_country[manual_processed$nbr_country>0 & manual_processed$mode=="sex"])))
)
```


##2. Does reproductive mode affect variables within genera? \newline (Manual + Digitalized)

###From manual dataset:

```{r genus_host_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}
par(mfrow=c(4,3))
for(i in levels(manual_processed$genus)[-c(7,9)])
{
  genus_df <- manual_processed[manual_processed$genus==i & manual_processed$mode!="both",]
  genus_df$mode <- factor(genus_df$mode)
  boxplot(genus_df[,"nbr_host_spp"]~genus_df$mode,main=paste(i, "Host species", sep=":"))
  text(x = c(1.1,2.1),y=c(mean(na.rm=T,genus_df$nbr_host_spp[genus_df$mode=="asex"])*1.1,mean(na.rm=T,genus_df$nbr_host_spp[genus_df$mode=="sex"])*1.1),labels=c(paste0("n=",length(genus_df[genus_df$mode=="asex" & !is.na(genus_df$nbr_host_spp),"lat_max"])),
                                        paste0("n=",length(genus_df[genus_df$mode=="sex" & !is.na(genus_df$nbr_host_spp),"lat_max"]))))
}

```

```{r genus_distribution_range_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}

par(mfrow=c(2,4))
latrange_diff <- c()
latrange_ratio <- c()
genname <- c()
for(i in levels(manual_processed$genus))
{
  gen_df <- manual_processed[manual_processed$genus==i & manual_processed$mode!="both",]
  gen_df <- subset(gen_df,subset = gen_df$nbr_country>0)
  gen_df$mode <- factor(gen_df$mode)
  if(length(gen_df$nbr_country[gen_df$nbr_country>0 & gen_df$mode =="asex"])>0 & length(gen_df$nbr_country[gen_df$nbr_country>0 & gen_df$mode =="sex"])>0)
  {
    my_names <-c(as.character(paste0("n=",length(gen_df[gen_df$mode=="asex" & !is.na(gen_df$nbr_country),"lat_max"]))),
                 as.character(paste0("n=",length(gen_df[gen_df$mode=="sex" & !is.na(gen_df$nbr_country),"lat_max"]))))
    diff <- gen_df[gen_df$nbr_country>0,"lat_max"]-gen_df[gen_df$nbr_country>0,"lat_min"]
    sexdiff <-gen_df[gen_df$mode=='sex' & gen_df$nbr_country>1,"lat_max"]-gen_df[gen_df$mode=='sex' & gen_df$nbr_country>1,"lat_min"]
    asexdiff <-gen_df[gen_df$mode=='asex' & gen_df$nbr_country>1,"lat_max"]-gen_df[gen_df$mode=='asex' & gen_df$nbr_country>1,"lat_min"]
    latrange_ratio <- append(latrange_ratio,median(asexdiff,na.rm = T)/median(sexdiff,na.rm = T))
    latrange_diff <- append(latrange_diff,median(asexdiff,na.rm = T)-median(sexdiff,na.rm = T))
    genname<- append(genname,i)
    #boxplot(diff~gen_df$mode[gen_df$nbr_country>0],main=paste(i, "Latitude range", sep=":"),
            #names = c(paste('asex',my_names[1],sep=': '),paste('sex',my_names[2],sep=': ')))
  }
  
}
```

```{r genus_distribution_range_diff_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
# df with asex-sex latranges I used diffferences instead of ratios because many values are close or == 0
df_latrange_diff <-data.frame(latrange_diff, genname)
df_latrange_ratio <-data.frame(latrange_ratio, genname)
library(lattice)
dotplot(df_latrange_diff$latrange_diff,main="Difference of latitude range between asex and sex per genus",xlab="Difference (asex-sex)")

```

```{r genus_distribution_range_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
dotplot(log(df_latrange_ratio$latrange_ratio),main="Log ratio of latitude ranges between asex and sex per genus", xlab="Log ratio (log(asex/sex))")

```

```{r genus_dist_median_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}


par(mfrow=c(2,4))
for(i in levels(manual_processed$genus))
{
  gen_df <- manual_processed[manual_processed$genus==i & manual_processed$mode!="both",]
  gen_df <- subset(gen_df,subset = gen_df$nbr_country>0)
  gen_df$mode <- factor(gen_df$mode)
  if(length(gen_df$nbr_country[gen_df$nbr_country>0 & gen_df$mode =="asex"])>0 & length(gen_df$nbr_country[gen_df$nbr_country>0 & gen_df$mode =="sex"])>0)
  {
    my_names <-c(as.character(paste0("n=",length(gen_df[gen_df$mode=="asex" & !is.na(gen_df$nbr_country),"lat_max"]))),
                 as.character(paste0("n=",length(gen_df[gen_df$mode=="sex" & !is.na(gen_df$nbr_country),"lat_max"]))))
    boxplot(gen_df[gen_df$nbr_country>0,"lat_median"]~gen_df$mode,main=paste(i, "Median latitude", sep=":"),names = c(paste('asex',my_names[1],sep=': '),paste('sex',my_names[2],sep=': ')))
  }
  
}
```

###From digitalized dataset:

```{r genus_host_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}
par(mfrow=c(4,3))
host_ratio <- c()
for(i in levels(auto_processed$genus))
{
  genus_df <- auto_processed[auto_processed$genus==i & auto_processed$mode!="both",]
  genus_df <- subset(genus_df,subset = genus_df$host_spp>0)
  genus_df$mode <- factor(genus_df$mode)
  if(length(genus_df$nbr_country[genus_df$host_spp>0 & genus_df$mode =="asex"])>0 & length(genus_df$nbr_country[genus_df$host_spp>0 & genus_df$mode =="sex"])>0)
  {
    tmp_ratio <- median(genus_df$host_spp[genus_df$host_spp>0 & genus_df$mode=='asex'])/median(genus_df$host_spp[genus_df$host_spp>0 & genus_df$mode=='sex'])
    host_ratio <- append(host_ratio,tmp_ratio)
    my_names <-c(as.character(paste0("n=",length(genus_df[genus_df$mode=="asex" & !is.na(genus_df$host_spp),"lat_max"]))),
                 as.character(paste0("n=",length(genus_df[genus_df$mode=="sex" & !is.na(genus_df$host_spp),"lat_max"]))))
    boxplot(genus_df$host_spp[genus_df$host_spp>0]~genus_df$mode[genus_df$host_spp>0],main=paste(i, "Latitude range", sep=":"),names = c(paste('asex',my_names[1],sep=': '),paste('sex',my_names[2],sep=': ')))
  }
}

```

```{r genus_host_ratio_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
dotplot(log(host_ratio), main="Log ratio (asex/sex) per genus of number of host species",xlab='Log ratio')
```

```{r genus_distribution_range_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}
par(mfrow=c(3,4))
latrange_diff <- c()
latrange_ratio <- c()
genname <- c()
for(i in levels(auto_processed$genus))
{
  genus_df <- auto_processed[auto_processed$genus==i & auto_processed$mode!="both",]
  genus_df$mode <- factor(genus_df$mode)
  if(length(genus_df$nbr_country[genus_df$nbr_country>1 & genus_df$mode =="asex"])>0 & length(genus_df$nbr_country[genus_df$nbr_country>1 & genus_df$mode =="sex"])>0)
  {
    my_names <-c(as.character(paste0("n=",length(genus_df[genus_df$mode=="asex" & !is.na(genus_df$nbr_country),"lat_max"]))),
                 as.character(paste0("n=",length(genus_df[genus_df$mode=="sex" & !is.na(genus_df$nbr_country),"lat_max"]))))
    diff <-genus_df[genus_df$nbr_country>1,"lat_max"]-genus_df[genus_df$nbr_country>1,"lat_min"]
    sexdiff <-genus_df[genus_df$mode=='sex' & genus_df$nbr_country>1,"lat_max"]-genus_df[genus_df$mode=='sex' & genus_df$nbr_country>1,"lat_min"]
    asexdiff <-genus_df[genus_df$mode=='asex' & genus_df$nbr_country>1,"lat_max"]-genus_df[genus_df$mode=='asex' & genus_df$nbr_country>1,"lat_min"]
    latrange_ratio <- append(latrange_ratio,median(asexdiff,na.rm = T)/median(sexdiff,na.rm = T))
    latrange_diff <- append(latrange_diff,median(asexdiff,na.rm = T)-median(sexdiff,na.rm = T))
    genname<- append(genname,i)
    boxplot(diff~genus_df$mode[genus_df$nbr_country>1],main=paste(i, "Latitude range", sep=":"),names = c(paste('asex',my_names[1],sep=': '),paste('sex',my_names[2],sep=': ')))
  }
}
```

```{r genus_distribution_range_diff_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
# df with asex-sex latranges I used diffferences instead of ratios because many values are close or == 0
df_latrange_diff <-data.frame(latrange_diff, genname)
df_latrange_ratio <-data.frame(latrange_ratio, genname)
library(lattice)
dotplot(df_latrange_diff$latrange_diff,main="Difference of latitude range between asex and sex per genus",xlab="Difference (asex-sex)")

```

```{r genus_distribution_range_ratio_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
dotplot(log(df_latrange_ratio$latrange_ratio),main="Log ratio of latitude ranges between asex and sex per genus", xlab="Log ratio (log(asex/sex))")
```

```{r genus_dist_median_auto, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}

par(mfrow=c(4,3))
medlat_ratio <- c()
for(i in levels(auto_processed$genus))
{
  genus_df <- auto_processed[auto_processed$genus==i & auto_processed$mode!="both",]
  genus_df <- subset(genus_df,subset = genus_df$nbr_country>0)
  genus_df$mode <- factor(genus_df$mode)
  if(length(genus_df$nbr_country[genus_df$nbr_country>0 & genus_df$mode =="asex"])>0 & length(genus_df$nbr_country[genus_df$nbr_country>0 & genus_df$mode =="sex"])>0)
  {
    tmp_ratio <- median(genus_df$lat_median[genus_df$nbr_country>0 & genus_df$mode=='asex'])/median(genus_df$lat_median[genus_df$nbr_country>0 & genus_df$mode=='sex'])
    medlat_ratio <- append(medlat_ratio,tmp_ratio)
    my_names <-c(as.character(paste0("n=",length(genus_df[genus_df$mode=="asex" & !is.na(genus_df$nbr_country),"lat_max"]))),
                 as.character(paste0("n=",length(genus_df[genus_df$mode=="sex" & !is.na(genus_df$nbr_country),"lat_max"]))))
    boxplot(genus_df$lat_median[genus_df$nbr_country>0]~genus_df$mode[genus_df$nbr_country>0],main=paste(i, "Median latitude", sep=":"),names = c(paste('asex',my_names[1],sep=': '),paste('sex',my_names[2],sep=': ')))
  }
}
densityplot(log(medlat_ratio), main="Log ratio (sex/asex) of median latitude",xlab='Log ratio')
```



##3. Does reproductive mode affect variables within pairs? \newline(Manual only)

###From manual dataset:
 
```{r pair_setup_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}
ratios <- list(c(), c(), c(), c(), c(), c())
for(i in 1:(length(levels(as.factor(manual_processed$pair)))-1))
{
  count <-1
  for(j in c("nbr_country", "nbr_host_spp", "lat_max", "lat_min", "lat_mean", "lat_median"))
  {
    tmp_ratio <- mean(na.rm = T,manual_processed[manual_processed$mode=='asex' & manual_processed$pair==i,j])/
      mean(na.rm = T, manual_processed[manual_processed$mode=='sex' & manual_processed$pair==i,j])
    ratios[[count]] <- append(ratios[[count]], tmp_ratio)
    count <- count + 1
  }
}
df_ratio <- data.frame(ratios)
colnames(df_ratio)<-c("nbr_country", "host_ratio","north_ratio", "south_ratio", "mean_ratio","median_ratio")

```

```{r pair_host_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
dotplot(log10(df_ratio$nbr_country),xlab ="Log ratio",main="Number of locations: asex/sex in each pair",panel=function(x, ...){
               panel.dotplot(x, ...)
               panel.abline(v=0)
             })


```

```{r pair_distribution_range_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=8,fig.width=8}

par(mfrow=c(2,4))
latrange_diff <- c()
latrange_ratio <- c()
genname <- c()
for(i in 1:max(manual_processed$pair))
{
  pair_df <- manual_processed[manual_processed$pair==i & manual_processed$mode!="both",]
  pair_df <- subset(pair_df,subset = pair_df$nbr_country>0)
  pair_df$mode <- factor(pair_df$mode)
  if(length(pair_df$nbr_country[pair_df$nbr_country>1 & pair_df$mode =="asex"])>0 & length(pair_df$nbr_country[pair_df$nbr_country>1 & pair_df$mode =="sex"])>0)
  {
    my_names <-c(as.character(paste0("n=",length(pair_df[pair_df$mode=="asex" & !is.na(pair_df$nbr_country),"lat_max"]))),
                 as.character(paste0("n=",length(pair_df[pair_df$mode=="sex" & !is.na(pair_df$nbr_country),"lat_max"]))))
    diff <- pair_df[pair_df$nbr_country>0,"lat_max"]-pair_df[pair_df$nbr_country>0,"lat_min"]
    sexdiff <-pair_df[pair_df$mode=='sex' & pair_df$nbr_country>1,"lat_max"]-pair_df[pair_df$mode=='sex' & pair_df$nbr_country>1,"lat_min"]
    asexdiff <-pair_df[pair_df$mode=='asex' & pair_df$nbr_country>1,"lat_max"]-pair_df[pair_df$mode=='asex' & pair_df$nbr_country>1,"lat_min"]
    latrange_ratio <- append(latrange_ratio,median(asexdiff,na.rm = T)/median(sexdiff,na.rm = T))
    latrange_diff <- append(latrange_diff,median(asexdiff,na.rm = T)-median(sexdiff,na.rm = T))
    genname<- append(genname,i)
    boxplot(diff~pair_df$mode[pair_df$nbr_country>0],main=paste(i, "Latitude range", sep=":"),
            names = c(paste('asex',my_names[1],sep=': '),paste('sex',my_names[2],sep=': ')))
  }
  
}
```

```{r pair_distribution_range_diff_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
# df with asex-sex latranges I used diffferences instead of ratios because many values are close or == 0
df_latrange_diff <-data.frame(latrange_diff, genname)
df_latrange_ratio <-data.frame(latrange_ratio, genname)
library(lattice)
densityplot(df_latrange_diff$latrange_diff,main="Difference of latitude range between asex and sex per pair",xlab="Difference (asex-sex)")

```

```{r pair_distribution_range_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log(df_latrange_ratio$latrange_ratio),main="Ratio of latitude range between asex and sex per pair",xlab="Log ratio (asex/sex)")
```




```{r pair_ratio_setup_and_host_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=8}

ratios <- list(c(), c(), c(), c(), c(), c(), c(), c(), c())
for(i in 1:(length(levels(as.factor(manual_processed$pair)))-1))
{
  count <-1
  for(j in c("nbr_host_spp", "lat_min", "lat_max", "lat_mean", "lat_median", "lon_min", "lon_max", "lon_mean", "lon_median"))
  {
    tmp_ratio <- mean(na.rm = T,manual_processed[manual_processed$mode=='asex' & manual_processed$pair==i,j])/
      mean(na.rm = T, manual_processed[manual_processed$mode=='sex' & manual_processed$pair==i,j])
    ratios[[count]] <- append(ratios[[count]], tmp_ratio)
    count <- count + 1
  }
}
df_ratio <- data.frame(ratios)
colnames(df_ratio)<-c("host_ratio","south_ratio", "north_ratio", "mean_lat_ratio","median_lat_ratio","west_ratio", "east_ratio", "mean_lon_ratio", "median_lon_ratio")
par(mfrow=c(3,3))
densityplot(log2(df_ratio$host_ratio), main="Number of host per pair: asex/sex", xlab="Log ratio")

```

```{r pair_south_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}

densityplot(log2(df_ratio$south_ratio), main="Ratio of min latitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_noth_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$north_ratio), main="Ratio of max latitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_mean_lat_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$mean_lat_ratio), main="Ratio of mean latitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_median_lat_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$median_lat_ratio), main="Ratio of median latitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_west_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$west_ratio), main="Ratio of min longitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_east_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$east_ratio), main="Ratio of max longitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_mean_lon_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$mean_lon_ratio), main="Ratio of mean longitude per pair: asex/sex", xlab="Log ratio")
```

```{r pair_median_lon_ratio_manual, echo=FALSE, error=FALSE, warning=FALSE,fig.height=3,fig.width=7}
densityplot(log2(df_ratio$median_lon_ratio), main="Ratio of median longitude per pair: asex/sex", xlab="Log ratio")
```


